\vspace{-0.8in}Brief Announcement: A Family of Leaderless Generalized-Consensus Algorithms

### 2016-02-12 podc16/paper2.tex
small fix

We say that a command $c$ in the domain of $m_p$ is \emph{executable} when no command $c$ which is not in the domain of $m_p$ can be reached from $c$ by recursively following $c$'s dependencies.
The local variable $m_p$ denotes a directed graph $g_p$ whose set of vertices $V\left( g_p \right)$ is the executable commands of $m_p$ and whose edges $E\left( g_p \right)$ are such that there is an edge from $c_1$ to $c_2$ iff $c_2 \in m_p\left[ c_1 \right]$ (i.e., $c_1$ depends on $c_2$). For example, if $m_p = \left[ c_1 \mapsto \aset{c_2,c_4}, c_2 \mapsto \aset{c_3}, c_3 \mapsto \aset{c_2}\right]$ then $V\left( g_p \right) = \aset{c_2,c_3}$ and $E\left( g_p \right) = \aset{\left( c_2,c_3 \right),\left( c_3,c_2 \right)}$.

>>>>

We say that a command $c$ in the domain of $m_p$ is \emph{executable} when no command $c'$ which is not in the domain of $m_p$ can be reached from $c$ by recursively following $c$'s dependencies.
The local variable $m_p$ denotes a directed graph $g_p$ whose set of vertices $V\left( g_p \right)$ is the executable commands of $m_p$ and whose edges $E\left( g_p \right)$ are such that there is an edge from $c_1$ to $c_2$ iff $c_2 \in m_p\left[ c_1 \right]$ (i.e., $c_1$ depends on $c_2$). For example, if $m_p = \left[ c_1 \mapsto \aset{c_2,c_4}, c_2 \mapsto \aset{c_3}, c_3 \mapsto \aset{c_2}\right]$ then $V\left( g_p \right) = \aset{c_2,c_3}$ and $E\left( g_p \right) = \aset{\left( c_2,c_3 \right),\left( c_3,c_2 \right)}$.
